\textbf{Audio Recorder Implemented on FPGA-based Hardware} \hfill \textbf{Academic Project}
\begin{itemize}
    \item Designed audio serialization and deserialziation modules leveraging combinational and sequential logic.
    \item Integrated custom modules with existing IP memory modules for audio recording and playback.
    \item Final solution enabled recording and playback of two seconds of audio to one of multiple selectable memory blocks.
\end{itemize}

\textbf{IaaS and Faas Cloud-based Autoscaling and Machine Learning Pipelines} \hfill \textbf{Academic Projects}
\begin{itemize}
    \item Designed multiple scalable cloud-based projects using various AWS features including S3, SQS, EC2, Lambda.
    \item Implemented a horizontally-scaling infrastructure to dynamically start and stop EC2 instances based on workload size.
    \item Leveraged Lambda to implement a pipeline to perform facial recognition on videos submitted via a web tier.
\end{itemize}

\textbf{Low Level Embedded Systems Programming} \hfill \textbf{Academic Projects}
\begin{itemize}
    \item Interacted with various sensors and actuators including motors, screens, accelerometers, gyroscopes, distance encoders.
    \item Implemented various modal models on the Pololu 3pi+ 2040 Robot to navigate up and down sloped terrain and follow pre-determined paths drawn on the ground.
    \item Implemented a game on an arm-based microcontroller using an LCD and accelerometer to direct a ball through a series of randomly generated mazes using tilt.
\end{itemize}

\textbf{Interpretive Emulators and Debugging Tools for Old Game Consoles} \hfill \textbf{Personal Project}
\begin{itemize}
    \item Implemented low-level emulators for the DMG-GameBoy and Nintendo Entertainment System in C/C++ from scratch using the SDL2 and Win32 libraries.
    \item Implemented software replicas for various components and instruction sets to mimic hardware functionality and quirks using publicly available reverse engineering information.
    \item Enabled step-by-step instruction tracing and memory analysis for debugging. Verified emulator accuracy using community-developed test ROMs to assess mimicry of console functionality and hardware bugs.
\end{itemize}
